---
title: "Project 5: Does body temperature vary in human subjects according to activity level?"
author: "Lauren Geary, Julia Curry, Conor Booth, Weihang Huang"
date: "2023-10-04"
output: html_document
bibliography: BibliographyModule5.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```
# Introduction
### Body Temperature Responses to Exercise

According to @7318608, during low intensity aerobic exercise, skin temperature over both the active and inactive muscles decreases and returning to normal values a few moments after rest. This finding is counter intuitive, because according to @sawka1993physiological, core temperature initially increases rapidly and subsequently increases at a reduced rate until heat loss equals heat production during exercise. We would like to investigate on the topic of whether body temperature vary in human subjects according to activity level.

# Results

DS18B20 Sensor is used to collect the body temperature data and then data of body temperature from the active and inactive conditions for all group members is combined into one table and them plotted the data for comparison.

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
dat.f <- list.files(pattern = "couch|active.csv") #find the files

dat.l <- list() #make an empty list

for(i in dat.f){
  met.dat<- unlist(strsplit(i,"_")) #split of the filename string
  who <- met.dat[1] #store the first element
  activity <- gsub(".csv","",met.dat[2]) #store second element, dropping CSV with gsub()
  dat.l[[i]]<- read_csv(i)%>%
    mutate(who=who,activity=activity) #read, then store data with additional columns of metada in list as position unique to i
  
}
dat <- do.call(rbind,dat.l) #combine the list into table

dat%>%
  ggplot()+geom_boxplot(aes(x=activity,y=degC))+facet_grid(.~who) #plot to see what we get
```

From the plot, it's clear that the body temperature during active state is lower than the body temperature during couch state for all four of our group members.

# Discussion
The results is consistent with the findings from the paper @7318608 that the skin temperature decreases instead of increases after exercise. Our first hypothesis to explain the decrease in skin temperature is that the evaporating cooling is enhanced during exercise. However, according to @7318608, fall in skin temperature during initial exercise was not due to increased cooling by evaporation, but by vascular-constriction, probably caused by non-thermal factors.

To investigate on the effect of level of activity on the *core* temperature of human, more advanced equipment and better experimental design is needed.

# Author Contributions

### Julia Curry 
Combined all the data from the group into one table. Found and cited a study in the introduction that explains "Core Temperature Responses to Exercise".

### Conor Booth
Proof reading and final touches.

### Lauren Geary
Generated .csv files with group data of active and inactive conditions. 

### Weihang Huang
Created the bibliography text file and modified the introduction wrote by Julia. Wrote the discussion session.

# Reference


