---
title: "Project 5: Does body temperature vary in human subjects according to activity level?"
author: "Lauren Geary, Julia Curry, Connor Booth, Weihang Huang"
date: "2023-10-04"
output: html_document
bibliography: BibliographyModule5.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
### Core Temperature Responses to Exercise

According to @7318608 ,during low intensity aerobic exercise, skin temperature over both active and inactive muscles decreases, returning to normal values  a few minutes after it. This finding is counterintuitive, because according to @sawka1993physiological, core temperature initially increases rapidly and subsequently increases at a reduced rate until heat loss equals heat production during exercise. We would like to investigate on the topic of whetherbody temperature vary in human subjects according to activity level?.

# Results
We combined data of body temperature from the active and inactive conditions for all group members into one table and them plotted the data for comparison.

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
dat.f <- list.files(pattern = "couch|active.csv") #find the files

dat.l <- list() #make an empty list

for(i in dat.f){
  met.dat<- unlist(strsplit(i,"_")) #split of the filename string
  who <- met.dat[1] #store the first element
  activity <- gsub(".csv","",met.dat[2]) #store second element, dropping CSV with gsub()
  dat.l[[i]]<- read_csv(i)%>%
    mutate(who=who,activity=activity) #read, then store data with additional columns of metada in list as position unique to i
  
}
dat <- do.call(rbind,dat.l) #combine the list into table

dat%>%
  ggplot()+geom_boxplot(aes(x=activity,y=degC))+facet_grid(.~who) #plot to see what we get
```

From the plot, it's clear that the body temperature during active state is lower than the body temperature during couch state for all four of our group members.

# Discussion
The results is not consistent with the results from the paper @sawka1993physiological , the body temperature decreases instead of increase after exercise.

# Author Contributions

### Julia Curry 
Combined all the data from the group into one table. Found and cited a study in the introduction that explains "Core Temperature Responses to Exercise".

### Connor Booth

### Lauren Geary
Generated .csv files with group data of active and inactive conditions. 

### Weihang Huang
Created the bibliography page from the reference found by Julia and pushed the introduction from Julia to the rmd profile.


# Reference


